Generalized spaces for constructive algebra

### 2020-04-08 paper-herrsching2019/main.tex
References on locales

\paragraph{Locales.}
% XXX \cite{belanger-marquis:pointless} and Johnstone, vickers:locales-toposes,
% picado-pultr:frames-and-locales

@@

Section~\ref{sect:locales} explores the basics of the theory of locales, with a
focus on examples and issues for constructive mathematics.

@@

XXX Cite http://www.mat.uc.pt/~picado/covariant/contents.pdf
http://www.mat.uc.pt/~picado/publicat/Chapter2.pdf

XXX Cite Frames and Locales: Topology Without Points

@@

FUTURE: Why the name "geometric"?
FUTURE: Forcing

>>>>

\paragraph{Locales.}

@@

Section~\ref{sect:locales} explores the basics of the theory of locales, with a
focus on examples and issues for constructive mathematics. Accessible
introductions to the theory include
Refs.~\refcite{johnstone:art,johnstone:point}. The interplay between logic and
geometry is particularly stressed in
Refs.~\refcite{vickers:continuity,vickers:locales-toposes}. We recommend
Ref.~\refcite{belanger-marquis:pointless} for a historical guide and
Ref.~\refcite{picado-pultr:frames-and-locales} for a comprehensive modern
textbook on the subject.

@@

@@

FUTURE: Why the name "geometric"?
FUTURE: Forcing
FUTURE: Grothendieck quote

% schuster:formal-zariski
% cls:spectral-schemes
really necessary? Wouldn't it suffice to define~$\Spec(A)$ as the topological
space of filters of~$A$? Indeed, for some time this was
believed~\cite[Section~3]{lawvere:icm-address}; however, this hope turned out
certain topos without any filters~\cite[pp.~200f.]{tierney:spectrum}, thus
